---
title: "Risk Management with R - Module 3 - Non-Normal Distributions"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

The code from the course was adapted using the [**tidyquant**](https://business-science.github.io/tidyquant/index.html) package as a way to better understand its workflow and functions. 

## Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(tidyquant)
library(skimr)
library(moments)
library(metRology)
library(MASS)
```


## 1. Non-normal Distributions

Loading Data

```{r}

#security = "GOLDPMGBD228NLBM"

security = "WILL5000IND"

wilsh <- tq_get(security, get = "economic.data", from = "1979-12-31", to  = "2017-12-31")

wilsh <- wilsh %>% 
  na.omit()

log_returns <- wilsh %>%
    group_by(symbol) %>%
    tq_transmute(select = price, 
                 mutate_fun = periodReturn, 
                 period     = "daily", 
                 col_rename = "d_return")

```

Analyzing returns:

```{r}

skim(log_returns)

#mean
(mu = mean(log_returns$d_return))

#standard deviation
(sig = sd(log_returns$d_return))


log_returns %>% 
  ggplot(aes(d_return)) +
  geom_density() +
  labs(title = "Distribution of Returns") + 
  theme_tq()

```


### 1.1. Skewness

- sk = 0 :  symmetric (normal)
- sk < 0 : left-skewed (left tail > right tail)
- sk > 0 : right-skewed

```{r}

rvec <- as.vector(log_returns$d_return)

(skewness(rvec))

```

### 1.2 Kurtosis

- Heavy-tailed distributions are called **leptokurtic**, and have  fatter tails than the normal distribution.

- Thin-tailed distributions are called **platykurtic**, and aren't very typical.

- krt = 3 : normal
- sk < 3 : thin-tailed
- sk > 3 : heavy-tailed

```{r}

(kurtosis(rvec))

```

### 1.3 Tests for normality

```{r}
jarque.test(rvec) #p-value = 0: reject normality

#qqplot()
```

## 2. Rescaled t-distribution
```{r}

n_out <- 100000

alpha <- 0.05

set.seed(123789)

t.fit <- fitdistr(rvec,"t")

rvec <- rt.scaled(n_out, mean = t.fit$estimate[1], sd = t.fit$estimate[2], df = t.fit$estimate[3])

var <- quantile(rvec, alpha)

es <- mean(rvec[rvec < var])

```

## 3. VaR and ES

### 3.1. Student-t Simulation - Sum of 10 1-day return

```{r}
set.seed(123789)

rvec <- rep(0,n_out)

for (i in 1:10){
  
  rvec <- rvec + rt.scaled(n_out, mean = t.fit$estimate[1], sd = t.fit$estimate[2], df = t.fit$estimate[3])
  
}

(var <- quantile(rvec, alpha))

(es <- mean(rvec[rvec < var]))

```


### 3.2. IID Simulation - Sum of 10 1-day return

Draw results from the data for simulation

```{r}

set.seed(123789)

rvec <- rep(0,n_out)



for (i in 1:10){
  rvec <- rvec + sample( as.vector(log_returns$d_return), n_out, replace = TRUE)
}

(var <- quantile(rvec, alpha))

(es <- mean(rvec[rvec < var]))


```


### 3.3. Block Simulation - Sum of 10 consecutive 1-day return

Draw results from the data for simulation

```{r}

n_out <- 100000

alpha <- 0.05

set.seed(123789)

rvec <- rep(0,n_out)

rdat <-  as.vector(log_returns$d_return)

posn <- seq(from = 1, to = length(rdat)-9, by = 1)

rpos <- sample(posn, n_out, replace = TRUE)


for (i in 1:10){
  rvec <- rvec + rdat[rpos]
  rpos = rpos + 1
}

(var <- quantile(rvec, alpha))

(es <- mean(rvec[rvec < var]))

```




