---
title: "Risk Management with R - Module 2 - Normal Distributions"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

The code from the course was adapted using the [**tidyquant**](https://business-science.github.io/tidyquant/index.html) package as a way to better understand its workflow and functions. 

## Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(quantmod)
library(tidyquant)
library(skimr)
```


## 1. Distribution of Returns

Loading Data

```{r}

#security = "GOLDPMGBD228NLBM"

security = "WILL5000IND"

wilsh <- tq_get(security, get = "economic.data", from = "1979-12-31", to  = "2017-12-31")

wilsh <- wilsh %>% 
  na.omit()

log_returns <- wilsh %>%
    group_by(symbol) %>%
    tq_transmute(select = price, 
                 mutate_fun = periodReturn, 
                 period     = "daily", 
                 col_rename = "d_return")

```

Analyzing returns:

```{r}

skim(log_returns)

#mean
(mu = mean(log_returns$d_return))

#standard deviation
(sig = sd(log_returns$d_return))


log_returns %>% 
  ggplot(aes(d_return)) +
  geom_density() +
  labs(title = "Distribution of Returns") + 
  theme_tq()

```


## 2. Value-at-Risk (VaR)

```{r}

alpha = 0.05

#normal distribuition quantile
var = round(qnorm(alpha, mu, sig),6)

```

Applying to the hedge fund example: 

- Investor capital: $100 million
- Bank: $900 million

```{r}
inv_cap = 100000
bank = 900000 

#var

(conf_level = (inv_cap + bank)*(exp(var)-1))

```

This means there's a 5% chance that the hedge fund will lose more than $`conf_level` millions a day.

## 3. Expected Shortfall (ES)

a.k.a. cVaR, AVaR or expected tail loss

```{r}

es = mu-sig*dnorm(qnorm(alpha,0,1),0,1)/alpha

```

the expected shortfall is `es*100`%.

Applying for the HF:

```{r}

(es_hf = (inv_cap + bank)*(exp(es)-1))

```

**If** stocks fall more than `var*100`, the average loss will be $`es_hf` million.

## 4. Simulations to estimate VaR and ES

Mostly useful for non-normal distributions and checking values.

### 4.1. Normal distribution

Steps:
- Draw 100.000 outcomes from N(mu, sig)
- **VaR** is the *alpha* quantile of the 100.000 outcomes 
- **ES** is the average of the worst *alpha* x 100.000 outcomes 

```{r}

n_out <- 100000

set.seed(123789)

rvec <- rnorm(n_out, mu, sig)

(var_s <- quantile(rvec, alpha))

(es_s <- mean(rvec[rvec < var_s]))

(es_hf_s = (inv_cap + bank)*(exp(es_s)-1))

```

As we can see, the results are very similiar to what was calculated before.

### 4.2. Observed distribuition:

```{r}

n_out <- 100000

set.seed(123789)

rvec <- sample(as.vector(log_returns$d_return), n_out, replace = TRUE)


(var_s_2 <- quantile(rvec, alpha))

(es_s_2 <- mean(rvec[rvec < var_s_2]))

(es_hf_s_2 = (inv_cap + bank)*(exp(es_s_2)-1))

```

**If** stocks fall more than `var_s_2*100`, the average loss will be $`es_hf_s_2` million.

The results are different, because the returns are **not** normally distributed. Meaning that the VaR and ES calculated assuming the normal distribution might be too small.





